Make manuscript figures

### 2021-10-29 scripts/R/make_manuscript_figures.rmd
fix black point in fig 2 to match actual POUMM estimate, add gwas results figure

Load data
```{r}
accuracy_simulation_results <- read.delim("output/2021-08-31_estimator_accuracy_MLE.txt")
tpr_simulation_results <- read.delim("output/2021-08-31_GWAS_TPR_MLE.txt")
tree <- ape::read.tree(file = paste(OUTDIR, "pathogen_no_outgroup.newick", sep = "/"))
traits <- read.csv(file = paste(OUTDIR, "poumm_corrected_traits.csv", sep = "/"))
tree <- treeio::full_join(tree, traits, by = "label")
POUMM_fit <- get(load(file = paste(OUTDIR, "POUMM_fit.RData", sep = "/")))
pc_scores <- read.csv(file = paste(OUTDIR, "shcs_vs_hapmap_pc_scores.csv", sep = "/"))
gwas_results <- read.delim(file = paste(OUTDIR, "gwas_results.pvals.effectsize.txt", sep = "/"), sep = "", header = T)
```

@@

Simulation results
```{r}
# Get POUMM values for HIV spVL to annotate plot with
spvl_data <- data.frame(
        inference.method = "h.MWA.p.value",
        H2 = 3.9,
        alpha = 8.046)  # values are hand-calculated because the breaks scale is defined as seq(0.5, n.breaks - 0.5, 1) in plotting function

>>>>

Load data
```{r}
accuracy_simulation_results <- read.delim("output/2021-08-31_estimator_accuracy_MLE.txt")
tpr_simulation_results <- read.delim("output/2021-08-31_GWAS_TPR_MLE.txt")
tree <- ape::read.tree(file = paste(OUTDIR, "pathogen_no_outgroup.newick", sep = "/"))
traits <- read.csv(file = paste(OUTDIR, "poumm_corrected_traits.csv", sep = "/"))
tree <- treeio::full_join(tree, traits, by = "label")
POUMM_fit <- get(load(file = paste(OUTDIR, "POUMM_fit.RData", sep = "/")))
poumm_parameter_estimates <- read.csv(file = paste(OUTDIR, "poumm_parameter_estimates.csv", sep = "/"))
pc_scores <- read.csv(file = paste(OUTDIR, "shcs_vs_hapmap_pc_scores.csv", sep = "/"))
gwas_results <- read.delim(file = paste(OUTDIR, "gwas_results.pvals.effectsize.txt", sep = "/"), sep = "", header = T)
```

@@

Simulation results
```{r}
# Get POUMM values for HIV spVL to annotate plot with
H2_estimate <- poumm_parameter_estimates[poumm_parameter_estimates$stat == "H2tMean", "PostMean"]
alpha_estimate <- poumm_parameter_estimates[poumm_parameter_estimates$stat == "alpha", "PostMean"]

# Breaks scale is defined as seq(0.5, n.breaks - 0.5, 1) in plotting function, need to translate real values to breaks scale
get_xval_for_sim_plots <- function(real_vals, estimate) {
      alpha_vals <-
      base_val <- rev(real_vals[real_vals < estimate])[1]
      next_val <- real_vals[real_vals > estimate][1]
      base_xval <- which(real_vals == base_val)
      next_xval <- which(real_vals == next_val)
      xval <- base_xval - 0.5 + (next_xval - base_xval) * (estimate - base_val) / (next_val - base_val)
      return(xval)
}

spvl_data <- data.frame(
        inference.method = "h.MWA.p.value",
        H2 = get_xval_for_sim_plots(real_vals = c(0.15, 0.25, 0.35, 0.45, 0.55, 0.65, 0.75), estimate = H2_estimate),
        alpha = get_xval_for_sim_plots(real_vals = c(0.1, 0.5, 1, 5, 10, 20, 30, 40, 50, 60), estimate = alpha_estimate))
